\huge A Usability Evaluation of Tor Launcher

### 2017-03-16 pets2017-paper/pets2017-paper.tex
Missing space.

There are studies that evaluated earlier forms of web browsing over Tor,
without a particular focus on configuration.
In 2012, Norcie et~al.~\cite{norcie2012eliminating}
investigated Tor Browser's``stop-points'' during installation and use,
which they define as places where users' uncertainty about what to do
put them at risk of not completing a task.
Of their 25 participants, 64\% encountered at least one stop-point,
such as a long startup time, misidentified icons, or confusion with other web browsers.

>>>>

There are studies that evaluated earlier forms of web browsing over Tor,
without a particular focus on configuration.
In 2012, Norcie et~al.~\cite{norcie2012eliminating}
investigated Tor Browser's ``stop-points'' during installation and use,
which they define as places where users' uncertainty about what to do
put them at risk of not completing a task.
Of their 25 participants, 64\% encountered at least one stop-point,
such as a long startup time, misidentified icons, or confusion with other web browsers.
